### 2014-10-29 motivation.tex
Minor edit

\begin{codehaskell}
data Acc = Deposit_ Int | Withdraw_ Int | GetBalance_

getBalance :: [Acc] -> () -> (Int, Maybe Acc)
getBalance ctxt _ =
  let res = sum [x | Deposit_ x <- ctxt]
						- sum [x | Withdraw_ x <- ctxt]
	in (res, Nothing)

deposit :: [Acc] -> Int -> ((), Maybe Acc)
deposit _ amt = (amt, Just $ Deposit_ amt)

withdraw :: [Acc] -> Int -> (Bool, Maybe Acc)
withdraw ctxt v =
	if sel1 $ getBalance ctxt () >= v
  then (True, Just $ Withdraw_ v)
	else (False, Nothing)
\end{codehaskell}

>>>>

\begin{codehaskell}
data Acc = Deposit Int | Withdraw Int | GetBalance

getBalance :: [Acc] -> () -> (Int, Maybe Acc)
getBalance ctxt _ =
  let res = sum [x | Deposit x <- ctxt]
						- sum [x | Withdraw x <- ctxt]
	in (res, Nothing)

deposit :: [Acc] -> Int -> ((), Maybe Acc)
deposit _ amt = (amt, Just $ Deposit amt)

withdraw :: [Acc] -> Int -> (Bool, Maybe Acc)
withdraw ctxt v =
	if sel1 $ getBalance ctxt () >= v
  then (True, Just $ Withdraw v)
	else (False, Nothing)
\end{codehaskell}
